### 2018-08-03 article.tex
Q-valued rewriting systems: Proposition 3 / Proposition 3 corollary

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM PROPOSITION 3        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{proposition}
$\catC(\mathbb{Q})$ is strictly symmetric monoidal with $\otimes$, the 2-functor of $\catC$.

\begin{proof}
The monoidal structure is immediate using the fact that
\[
F(r) \oplus F(s) \succeq F(r \otimes s)
\]
that is
\[
F(r: f \Rightarrow g) \oplus F(s: f' \Rightarrow g') = F(r \otimes s: f \otimes f' \Rightarrow g \otimes g')
\]
so
\[
\catE(f, g) \oplus \catE(f', g') = \catE(f \otimes f', g \otimes g')
\]
For the symmetry, we use the fact that $F(f \Rightarrow g) \oplus F(g \Rightarrow f) = e$
\begin{align}
\catE(f \otimes g, g \otimes f) &= F(f \otimes g \Rightarrow g \otimes g) \cr
&= F(f \Rightarrow g \otimes g \Rightarrow f) \cr
&\preceq F(f \Rightarrow g) \oplus F(g \Rightarrow f) \cr
&= F(f) \oplus F(g)^{-1} \oplus F(g) \oplus F(f)^{-1} \cr
&= e
\end{align}
\end{proof}
\end{proposition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM PROPOSITION 3 COROLLARY        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{corollary}
Given $s: f \Rightarrow g$ a transformation, and $s^{-1}: g \Rightarrow f$ the inverse transformation
\[
F(s \otimes s^{-1}) = e
\]
\end{corollary}
